---
title: "1_DataCleaning_RewardOnline"
author: "Austin Luor"
date: "7/2/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This is the analysis r-markdown to online version of reward money using Gorilla.sc. 
#Scoring data
##Setting up Environment
```{r, warning= FALSE, echo=FALSE, eval=FALSE}
library(ggplot2)
library(dplyr)
library(ggpubr)
library(ggridges)
library(tidyr)
library(forcats)
library(patchwork)
remotes::install_github("autoscore/autoscore"); library(autoscore)


#Downloaded from gorilla as raw data. Old is version 9 (n=10), new is version 10 (n=40). This can be found in the data folder in online reward projects. 
old <- read.csv("/Users/austinluor/Box/PeelleLab/research_projects/201901083_onlineReward01/shared/data/data_exp_14612-v9_task-55ha.csv")
new <- read.csv("/Users/austinluor/Box/PeelleLab/research_projects/201901083_onlineReward01/shared/data/data_exp_14612-v10_task-55ha.csv")

#Combine both dataframe into one data. 
data <- rbind(old, new)

#Trim the dataframe to have the right columns 
#This removes those rows that have "No source sound files".
data <- filter(.data=data, complete.cases(data$Reaction.Time))

#Trim the dataframe to have the right columns 
data<- data[,c(12,29,37,45,48,49,53,54)]

#Filter by the complete cases of response
data <- filter(.data=data, complete.cases(data$Response))

#Filter by the complete cases of randomise_block (To remove the practice trials and those who have loading delays)
data <- filter(.data=data, complete.cases(data$randomise_blocks))


#Filter by the complete cases of response
Response <- seq(3, nrow(data), 4)
data<- data[Response,]


#For those that have loading delays, it is likely that their trial will rerun resulting in duplicate trial numbers. This attempts to remove rows that have duplicated row trial numbers. 
data <-data[with(data, c(data$Trial.Number[-1]!= data$Trial.Number[-nrow(data)], TRUE)),]
```


###Preprocessing for Autoscore

This section of the code uses the R package: Autoscore. In order to use this package, you will have to change the format of your dataframe that is compartible to use the Autoscore pacakge online. 

The order of procedures:
1. Shorten the dataframe to: ID, trial number, response, target,...)
2. For the target column, remove all the "the", "a", or remove everything that is not captialize
3. Export it to csv.


```{r, echo=FALSE, eval=FALSE}
#Shorten the dataframe to the columns that I need
data <- data[,c(1:3,8)]

#Change the column name to match Autoscore format
names(data)[1] <- "id"
names(data)[4] <- "target"

#Remove the T in the target column
data$target <- gsub("The", "the", data$target)

#Replacing Gray with Gray and Grey so it will take count both spelling as correct
data$target <- gsub("GRAY", "GRAY GREY", data$target)


#Remove everything that is not capitalize in the target column.
data$target <- gsub("[a-z]", "", data$target)

#Removing extra white spaces so autoscore package can score accurately. 
data$target <- gsub("\\s+"," ", data$target)


#Add another row noting the reward cue for each subject
data$RewardCue <- "0"
data$RewardCue[data$Trial.Number == c(17:20, 37:40, 57:60, 77:80)] <- "$$$"

#Use Autoscore package to score
data <- autoscore(data)

```


###All Data Summary
You can analyze more than one subject on autoscore and it will spit out a meta data file with all of your data analyzed. You will be able to see how each of your participant's performance based on the ID column. 


```{r, warning=FALSE, echo=FALSE}
#Calculate how much each participant gets for the reward trials. Since there are 4 target words in each sentence, each word correct is counted for 15.625 cents. The total will be rounded. 
#Create a new column called cents and place 0 for every cell
data$cents <- 0

#For every cell that is a reward trial, write in 15.626 cents
data$cents[data$rewardcue != "0"] <- 15.625

#Multiply the 15.625 cents to the number of words answered correctly 
data$cents <- data$cents * data$autoscore


#Add another Participant ID number to the prolific/gorilla ID. Make sure to change the 1:n by how many participants we have
#Renaming the Px ID Column to 001~100
data$ParticipantID <- NA
for (i in unique(data$ParticipantID)) {
  data$ParticipantID <- rep(1:50, each=80)
}


#Reclassifying variables
data$id <- as.factor(data$id)
data$ParticipantID <- as.character(data$ParticipantID)
data$autoscore <- as.numeric(data$autoscore)
data$cents <- as.numeric(data$cents)

#Convert autoscore column into percentages/If you want to keep this as 1~4, don't run this line.
data$autoscore <- data$autoscore * 25

#Rearranging Participant ID column
data <- data[,c(8,1:7)]

#######CHECK POINT######
#This export all participant's raw data/responses, autoscore, reward trials for plotting and modeling purposes.
write.csv(data, "/Users/PATH/alldatasummary.csv")

```
