---
title: "OnlineRewardGorillaScript"
author: "Austin Luor"
date: "4/15/2020"
output:
  pdf_document: default
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

This is the analysis r-markdown to online version of reward money using Gorilla.sc. 
#Scoring data
##Setting up Environment
```{r, warning= FALSE, echo=FALSE, eval=FALSE}
library(ggplot2)
library(dplyr)
library(ggpubr)
library(ggridges)
library(tidyr)
library(forcats)
library(patchwork)

#data <- readxl::read_xlsx("/Users/austinluor/Desktop/data_exp_14612-v10_task-55ha.xlsx")

#data <- readxl::read_xlsx("/Users/austinluor/Desktop/Errorfiles.xlsx")
old <- readxl::read_xlsx("/Users/austinluor/Desktop/data_exp_14612-v9_task-55ha_old10.xlsx")
new <- readxl::read_xlsx("/Users/austinluor/Desktop/data_exp_14612-v10_task-55hanew40.xlsx")

data <- rbind(old, new)

write.csv(data, "/Users/austinluor/Desktop/alldataraw.csv")
#Trim the dataframe to have the right columns 
#data <- data[,-c(1:10)]

#This removes those rows that have "No source sound files".
data <- filter(.data=data, complete.cases(data$`Reaction Time`))

#Trim the dataframe to have the right columns 
data<- data[,c(12,29,37,45,48,49,53,54)]

#Filter by the complete cases of response
data <- filter(.data=data, complete.cases(data$Response))

#Filter by the complete cases of randomise_block (To remove the practice trials and those who have loading delays)
data <- filter(.data=data, complete.cases(data$randomise_blocks))

#For those that have loading delays, it is likely that their trial will rerun resulting in duplicate trial numbers. This attempts to remove rows that have duplicated row trial numbers. 
data <-data[with(data, c(data$`Trial Number`[-1]!= data$`Trial Number`[-nrow(data)], TRUE)),]
```


###Preprocessing for Autoscore

This section of the code uses the R package: Autoscore. In order to use this package, you will have to change the format of your dataframe that is compartible to use the Autoscore pacakge online. 

The order of procedures:
1. Shorten the dataframe to: ID, trial number, response, target,...)
2. For the target column, remove all the "the", "a", or remove everything that is not captialize
3. Export it to csv.


```{r, echo=FALSE, eval=FALSE}
#Shorten the dataframe to the columns that I need
data <- data[,c(1:3,8)]

#Change the column name to match Autoscore format
names(data)[1] <- "id"
names(data)[4] <- "target"

#Remove the T in the target column
data$target <- gsub("The", "the", data$target)

#Replacing Gray with Gray and Grey so it will take count both spelling as correct
data$target <- gsub("GRAY", "GRAY GREY", data$target)


#Remove everything that is not capitalize in the target column.
data$target <- gsub("[a-z]", "", data$target)

#Removing extra white spaces so autoscore package can score accurately. 
data$target <- gsub("\\s+"," ", data$target)


#Add another row noting the reward cue for each subject
data$RewardCue <- "0"
data$RewardCue[data$`Trial Number` == c(17:20, 37:40, 57:60, 77:80)] <- "$$$"


```

###Concatenating all other subjects' data into one file

```{r, echo=FALSE, eval=FALSE}
##Install autoscore
remotes::install_github("autoscore/autoscore"); library(autoscore)

##
#acceptable <- as.data.frame(read.csv("/Users/austinluor/Desktop/acceptable_spellings.csv"))

#Use Autoscore package to score
data <- autoscore(data)

```

#################################
From this section and on, you should be working with a meta data that consists of all the subjects in ONE excel sheet. 
#################################

###PostProcessing from Autoscore
You can analyze more than one subject on autoscore and it will spit out a meta data file with all of your data analyzed. You will be able to see how each of your participant's performance based on the ID column. 

In this section,  I will add several columns to calculate the final earned total and also prepared the data for plotting. Before you read in your metadata, make sure you remove the first row in the xlsx file. 

```{r, warning=FALSE, echo=FALSE}
#reading in Meta Data (file spit out from Autoscore)
data

#Calculate how much each participant gets for the reward trials. Since there are 4 target words in each sentence, each word correct is counted for 15.625 cents. The total will be rounded. 
#Create a new column called cents and place 0 for every cell
data$cents <- 0

#For every cell that is a reward trial, write in 15.626 cents
data$cents[data$rewardcue != "0"] <- 15.625

#Multiply the 15.625 cents to the number of words answered correctly 
data$cents <- data$cents * data$autoscore

#Find the sum and then just multiply 15.625 to it. Divide it by 100 and round it to the nearest dollar
# round(sum(data$cents)/100)

#To find out how much a specific participant made; filter based on participants PROBLEM
# data %>% filter(data$id == "1") %>% round(sum(data$cents))


#Renaming the Px ID Column to 001~100
data$ParticipantID <- NA
#Add another Participant ID number to the prolific/gorilla ID. Make sure to change the 1:n by how many participants we have
for (i in unique(data$ParticipantID)) {
  data$ParticipantID <- rep(1:50, each=80)
}


#Reclassifying variables
data$id <- as.factor(data$id)
data$ParticipantID <- as.character(data$ParticipantID)
data$`trial number` <- as.numeric(data$`trial number`)
data$autoscore <- as.numeric(data$autoscore)
data$cents <- as.numeric(data$cents)

#names(data)[6] <- "trialnumber"

#Convert autoscore column into percentages
data$autoscore <- data$autoscore * 25


#######CHECK POINT######
#This export all participant's raw data/responses, autoscore, reward trials etc. 
write.csv(data, "/Users/austinluor/Desktop/alldatasummary.csv")


```


#Plotting

##Average percentage accuracy for each of the 80 trials.
```{r, warnings= FALSE}
averagefortrials <- NA
trial <- c(1:80)
block <- NA
fortrials <- data.frame(averagefortrials, trial, block, stringsAsFactors=FALSE)

for (i in data$`trial number`){
 fortrials[i,1]<-mean(data$autoscore[data$`trial number` == i])
}


# #Line graph for all participants as a function of trials; could also add vertical shapdes to show where the reward trials are
  
pdf("/Users/austinluor/Desktop/allTrialsAverage")
ggplot(fortrials, aes(x=trial, y=averagefortrials)) +
  #geom_smooth(aes(y=fortrials$averagefortrial), se=TRUE, color="#00BFC4") +
  geom_line(aes(y=averagefortrials),color="#758BFD") +
  theme_classic() +
  scale_y_continuous(breaks = c(0, 25, 50, 75, 100), limits = c(-10,110)) +
  labs(label = 'percent') +
  labs(x='Trials', y='Accuracy (% correct)', title = "Average accuracy of each trial for all 50 participants") +
  annotate("rect", xmin = 17, xmax = 20, ymin = -10, ymax = 100, alpha = .2) +
  annotate("rect", xmin = 37, xmax = 40, ymin = -10, ymax = 100, alpha = .2) +
  annotate("rect", xmin = 57, xmax = 60, ymin = -10, ymax = 100, alpha = .2) +
  annotate("rect", xmin = 77, xmax = 80, ymin = -10, ymax = 100, alpha = .2)

dev.off()

```


```{r, echo=FALSE}
  


#Line graph for all participants as a function of trials; could also add vertical shapdes to show where the reward trials are
  # ggplot(data, aes(x=`trial number`, y=autoscore, color = ParticipantID, group = ParticipantID)) +
  # geom_smooth(aes(y=data$autoscore), se=FALSE, alpha=0.2) + 
  # #geom_line(aes(y=data$autoscore)) +
  # theme_classic() +
  # scale_y_continuous(breaks = c(0, 25, 50, 75, 100), limits = c(-10,110)) +
  # labs(label = 'percent') +
  # labs(x='Trials', y='Accuracy (% correct)', title = "All Participant") + 
  # annotate("rect", xmin = 17, xmax = 20, ymin = -10, ymax = 100, alpha = .2) +
  # annotate("rect", xmin = 37, xmax = 40, ymin = -10, ymax = 100, alpha = .2) +
  # annotate("rect", xmin = 57, xmax = 60, ymin = -10, ymax = 100, alpha = .2) +
  # annotate("rect", xmin = 77, xmax = 80, ymin = -10, ymax = 100, alpha = .2) + 
  # scale_fill_viridis_c()


```


#Data Analysis

###Average of two types of trials

```{r, warning=FALSE, echo=TRUE, eval=TRUE}
#Creating a new dataframe that stores everyone's averages 
ID <- c(1:50)
noreward <- NA
reward <- NA
average.data <- data.frame(ID, noreward, reward, stringsAsFactors=FALSE)

# 
for (i in unique(data$ParticipantID)) {
  average.data[i, 2] <- mean(data$autoscore[data$ParticipantID == i & data$rewardcue =="0"])
  average.data[i, 3] <- mean(data$autoscore[data$ParticipantID == i & data$rewardcue =="$$$"])
  #average.data[i, 4] <- (sum(data$cents[data$id == i & data$rewardcue =="$$$"])/100)
}


#Find the average of non reward trials for each participant
# average.data[1,2] <- mean(data$autoscore[data$id == '1' & data$rewardcue =="0"])
# average.data[1,3] <- mean(data$autoscore[data$id == '1' & data$rewardcue =="$$$"])
# 
# average.data[2,2] <- mean(data$autoscore[data$id == '2' & data$rewardcue =="0"])
# average.data[2,3] <- mean(data$autoscore[data$id == '2' & data$rewardcue =="$$$"])

#write.csv(average.data, "/Users/austinluor/Desktop/ParticipantConditionAccur.csv")


#Gathering the dataframe to plot boxplot. 
# average.data %>% gather(key=Conditions, value=Accuracy, -ID) %>% ggplot(aes(x=Conditions, y=Accuracy, fill=Conditions)) + geom_boxplot(width=0.1) + scale_fill_brewer() + theme_classic() + geom_point(aes(x=Conditions, y=Accuracy), alpha=0.5)

#Or
pdf("/Users/austinluor/Desktop/Paired")
ggpaired(average.data, cond1 = "noreward", cond2 = "reward", color = "condition", width = 0.1, line.color = "gray", line.size = 0.4, palette = "npg") + stat_compare_means(paired = TRUE, label.x = 0.6) + ylim(0,100)

dev.off()
#parametric paired t-test
t.test(average.data$noreward, average.data$reward, paired=TRUE)
#non-parametric comparison
wilcox.test(average.data$noreward, average.data$reward, paired = TRUE)

```

### Finding the difference of Reward - no reward (Improvement index)
```{r, eval= TRUE, echo=TRUE}
ID <- c(1:50)
noreward <- NA
reward <- NA
average.data <- data.frame(ID, noreward, reward, stringsAsFactors=FALSE)


for (i in unique(data$ParticipantID)) {
 average.data[i, 2] <- mean(data$autoscore[data$ParticipantID == i & data$rewardcue =="0"])
 average.data[i, 3] <- mean(data$autoscore[data$ParticipantID == i & data$rewardcue =="$$$"])
 #average.data[i, 4] <- (sum(data$cents[data$id == i & data$rewardcue =="$$$"])/100)
}


improvement <- average.data %>% mutate(difference = average.data$reward - average.data$noreward, mycolor = ifelse(difference>0, "improve", "worse"), Improvement = "Difference")


#Geom_Segment plot to see the difference between reward - noreward. In the order of rank, from greatest improvement to least improvement
pdf("/Users/austinluor/Desktop/PerformanceDifference")

improvement %>%
  arrange(-difference , ID) %>% # sort data based on group and value
  mutate(rank = row_number()) %>% # this will be used as x axis
  ggplot(aes(x=rank,y=difference),color=mycolor) +
  geom_segment(aes(x=rank, xend=rank, y=0, yend=difference, color=mycolor), size=2, alpha=0.9) +
  theme_light() + 
  theme(legend.position = "none", panel.border = element_blank()) + 
  theme(panel.grid.major.x = element_blank(), panel.border = element_blank()) +
  ylim(-20,20) +
  scale_colour_manual(values=c("#00BFC4","#F8766D"),labels = c("Improved","Worsen")) +
  xlab("Rank") +
  ylab("Percentage Difference (Reward - No reward) ") + labs(color = "") + 
  ggtitle(label = "Difference between Reward vs No reward Condition (n=50)") +
  theme(legend.position = c(0.95, 0.95), legend.justification = c("right", "top"))

dev.off()


#Geom_Segment plot to see the difference between reward - noreward. Not in the order of rank
ggplot(improvement, aes(x=ID, y=difference)) +
  geom_segment(aes(x=ID, xend=ID, y=0, yend=difference, color=mycolor), size=2, alpha=0.9) +
  theme_light() +
  theme(
    legend.position = "none",
    panel.border = element_blank(),
  ) + 
  theme(
    panel.grid.major.x = element_blank(),
    panel.border = element_blank()) + 
  scale_colour_manual(values=c("#00BFC4","#F8766D")) +
  xlab("Rank") +
  ylab("Percentage Difference (Reward - No reward) ")


#Histogram of differneces. Count/freq is on the y-axis and binned to 5% intervals. 
pdf("/Users/austinluor/Desktop/improvementDifferencedist")
hist(improvement$difference)
dev.off()

```



#Calculating Bonus payment 
```{r, eval=FALSE, echo=FALSE}
#Creating a new dataframe for bonus payment
ID <- c(1:50)
bonus <- NA
bonuspayment.data <- data.frame(ID, bonus, stringsAsFactors=FALSE)

#Loop for calculating the sum of each participant's bonus cents on reward trials. In dollar unit
for (i in unique(data$ParticipantID)) {
  bonuspayment.data[i, 2] <- (sum(data$cents[data$ParticipantID == i & data$rewardcue =="$$$"])/100)
}


#creating another short dataframe that matches prolific id to bonus payment
#Gathering data so participantid and prolific id gets to long format
matchid <- data[,c(1,4,6,8)]  %>% gather(key=acc,value=response, -id, -ParticipantID)

#filter out the unique items in participant ID and Prolific ID
matchid <- matchid[,c(1:2)] %>% unique.data.frame()

#Attach the prolific id to the bonuspayment dataframe.
bonuspayment.data$ProlificID <- matchid[,1]

#Filter it by the complete cases of bonus reward
bonuspayment.data <- bonuspayment.data %>% filter(complete.cases(bonus))

#View the dataframe
bonuspayment.data %>% skimr:::pander()

#Reordering the columns so prolific registers the bonus payment. 
bonuspayment.data<-bonuspayment.data[,c(1,3,2)]

#######CHECK POINT######
write.csv(bonuspayment.data, "/Users/austinluor/Desktop/BONUSPAYMENTONLINE.csv")


```


#Exploratory Analysis

##Combining all info and export it to all data summary for Sara to add Auxiliary measures. 
```{r, eval=FALSE}

average.data$improvement <- as.numeric(improvement$difference)

average.data$Prolific <- bonuspayment.data$ProlificID

average.data$cesdr <- as.numeric(cesdr$Response)

#average.data<-average.data[,c(1,5,2,3,4,6)]

write.csv(average.data, "/Users/austinluor/Desktop/alldatasummary.csv")

```


```{r, warning=FALSE, message=FALSE}
#Combining data from version 9 and version 10
cesdr <- readxl::read_xlsx("/Users/austinluor/Downloads/CESDR.xlsx")
cesdrold10 <- readxl::read_xlsx("/Users/austinluor/Downloads/CESDRold10.xlsx")

#Creating one data from oth excels 
cesdr <- rbind(cesdrold10, cesdr)
#Filtering out essential rows
cesdr <- cesdr[,c(12,27,28)] %>% filter(complete.cases(cesdr$Response))
#Grab the final CESDR score for all
cesdr <- cesdr[cesdr$`Question Key`=="CESDscore",] 


####Plotting
pdf("/Users/austinluor/Desktop/Online_Reward_Figures/CESD1")
ggplot(average.data, aes(x=reward, y=cesdr)) +
  geom_point(alpha=0.8, size=2) + 
  geom_smooth(method=lm, se=FALSE, alpha=0.3, color='black')+
  theme_classic() +
  labs(title = "Average Reward Acc vs CESDR") +
  xlab("Reward Trials % Accuracy") + 
  ylab("CESDR") + stat_cor(method = "pearson", label.x = 30, label.y = 50, size =3)

dev.off()
pdf("/Users/austinluor/Desktop/Online_Reward_Figures/CESD2")
ggplot(average.data, aes(x=noreward, y=cesdr)) +
  geom_point(alpha=0.8, size=2) + 
  geom_smooth(method=lm, se=FALSE, alpha=0.3, color='black')+
  theme_classic() +
  labs(title = "Average no-Reward Acc vs CESDR") +
  xlab("No Reward Trials % Accuracy") + 
  ylab("CESDR") + stat_cor(method = "pearson", label.x = 30, label.y = 50, size =3)
dev.off()

pdf("/Users/austinluor/Desktop/Online_Reward_Figures/CESD3")

ggplot(average.data, aes(x=improvement, y=cesdr)) +
  geom_point(alpha=0.8, size=2) + 
  geom_smooth(method=lm, se=FALSE, alpha=0.3, color='black')+
  theme_classic() +
  labs(title = "Improvement Acc vs CESDR") +
  xlab("Improvement % Accuracy") + 
  ylab("CESDR") + stat_cor(method = "pearson", label.x = 0, label.y = 50, size =3)
dev.off()

(x|y|z)
dev.off()
```